CODE CHECK

### 2020-01-24 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...

@@

- need to get wording straight: process/implementation/workflow (DN: suggest to use "workflow" for research-analysis workflow)
- https://codecheck.org.uk/process/
- _dimensions_ along which a check can vary
- independent/pre-submission (Peer_Coding) by author + colleagues
- AGILE
- premier (OA) publisher
- community OA / scholarly society with public peer review
- invited reproducibility paper track, cf. https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors
- on giving credit: public databases
  - https://www.reviewercredits.com/
  - Publons
  - ORCID
- compare with existing processes that are publicly documented
  - AJPS Verification Policy: https://ajps.org/ajps-verification-policy/
  - ...

>>>>

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html

@@

- need to get wording straight: process/implementation/workflow (DN: suggest to use "workflow" for research-analysis workflow)
- https://codecheck.org.uk/process/
- _dimensions_ along which a check can vary
- independent/pre-submission (Peer_Coding) by author + colleagues
- AGILE
- premier (OA) publisher
- community OA / scholarly society with public peer review
- invited reproducibility paper track, cf. https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors
- on giving credit: public databases
  - https://www.reviewercredits.com/
  - Publons
  - ORCID
- compare with existing processes that are publicly documented
  - AJPS Verification Policy: https://ajps.org/ajps-verification-policy/
  - ...
- flexible level of detail? a check can be enhanced to (potentially semi-automatically) check for good practices
  - "A group of us in the @force11rescomm Software Citation Implementation Working Group produced a "Software Citation Checklist for Authors" https://t.co/4Noe66FsoX providing guidelines on how to cite software and describing why it is important and what software should be cited" via https://twitter.com/alegonbel/status/1207664922932453376?s=09)
